Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-13 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Change "pair" to "interval-valued function"...

\begin{definition}We say a pair\nb$\left(\mathscr{I},\iota\right)$
is additive if $\mathscr{I}$ is a collection of intervals and $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is a function satisfying the following properties. 
\begin{itemize}
\item $\iota\left(0\right)=\left[0,0\right]$. 
\item $\iota\left(1\right)=\left[1,1\right]$. 
\item For any $x\in\left[0,1\right]$, $\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$. 
\item For a set\nb$\left\{ x_{i}\right\} _{i=1}^{N}\subseteq\left[0,1\right]$,
if $\sum_{i=1}^{N}x_{i}\in\left[0,1\right]$, then $\iota\left(\sum_{i=1}^{N}x_{i}\right)\subseteq\sum_{i=1}^{N}\iota\left(x_{i}\right)$. 
\end{itemize}
Moreover, $\left(\mathscr{I},\iota\right)$ is called convex if for
any three numbers\nb$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$ implies $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.\end{definition}

Although a convex pair\nb$\left(\mathscr{I},\iota\right)$ may look
exotic, the left end of $\iota$, defined by $\iotal\left(x\right)=\min\iota\left(x\right)$,
is well-studied Wright-convex satisfying $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,Pales2013}.
After we define\nb$\left(\mathscr{I},\iota\right)$, we are ready
to construct a QIVPM from a quantum probability measure.

\begin{lemma}\label{lemma:real2interval}Consider an additive pair\nb$\left(\mathscr{I},\iota\right)$.
Then, given a quantum probability measure\nb$\mu:\events\rightarrow\left[0,1\right]$,
a function\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined by
$\bar{\mu}\left(P\right)=\iota\left(\mu\left(P\right)\right)$ is
a quantum IVPM. Moreover, if $\left(\mathscr{I},\iota\right)$ is
convex, then $\bar{\mu}$ is convex.\end{lemma}

@@

\begin{lemma}Consider an additive pair\nb$\left(\mathscr{I},\iota\right)$.
Then, there is a quantum IVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.
Obviously, if $\left(\mathscr{I},\iota\right)$ is convex, so does
$\bar{\mu}$.\end{lemma}

@@

\begin{example}\label{ex:regular-pair}For any positive integer~$n$,
there is an additive pair\nb$\left(\mathscr{I}_{n},\iota_{n}\right)$
defined by 
\begin{equation}\eqalign{ 
\mathscr{I}_{n} = \set{\left[\frac{k}{n},\frac{k}{n}\right]}{k=0,\ldots,n}\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}\\ 
\iota_{n}\left(x\right) = \cases{ 
\left[\frac{k}{n},\frac{k}{n}\right] & , if $x=\frac{k}{n}$ ;\\ 
\left[\frac{k}{n},\frac{k+1}{n}\right] & , if $\frac{k}{n}<x<\frac{k+1}{n}$ . 
} 
}\end{equation}
Notice that the usual $\left\{ \necess,\imposs,\unknown\right\} $
is $\mathscr{I}_{1}$. Also, let $\mathscr{I}_{\infty}=\set{\left\{ x\right\} }{x\in\left[0,1\right]}$
and $\iota_{\infty}\left(x\right)=\left\{ x\right\} $. Of course,
$\left(\mathscr{I}_{\infty},\iota_{\infty}\right)$ is an additive
pair.\end{example}

@@

Although a convex QIVPM can be constructed by a convex pair easily,
any convex pair either is $\left\{ \necess,\imposs,\unknown\right\} $
or contains infinitely many intervals. The reason is that a Wright-convex
function is midpoint-convex or Jensen-convex, i.e., 
\begin{equation}
\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\textrm{ ,}
\end{equation}
and a midpoint-convex function is continuous on an open interval if
we cannot use the Axiom of Choices\nb\cite{Blumberg_1919,Sierpinski1920,RobertsVarberg1973}.

Even if an additive pair\nb$\left(\mathscr{I},\iota\right)$ is not
convex, it may still induce a convex QIVPM. In particular, every QIVPM
on a three-dimensional Hilbert space is convex by theorem~\ref{thm:convex-3}.
The next natural question is whether a non-convex pair always induces
some non-convex QIVPM, and the answer is ``yes'' by the following
lemma.

\begin{lemma}Given an additive but non-convex pair\nb$\left(\mathscr{I},\iota\right)$,
there is a non-convex quantum IVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$.\end{lemma}

@@

In conclusion, we may still use an additive but non-convex pair to
construct QIVPMs, but we need to verify the convexity of the constructed
QIVPM one-by-one which might be long and tedious.

>>>>

\begin{definition}Given $\mathscr{I}$ is a collection of intervals,
we say a interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is additive if $\iota$ satisfies the following properties. 
\begin{itemize}
\item $\iota\left(0\right)=\left[0,0\right]$. 
\item $\iota\left(1\right)=\left[1,1\right]$. 
\item For any $x\in\left[0,1\right]$, $\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$. 
\item For a set\nb$\left\{ x_{i}\right\} _{i=1}^{N}\subseteq\left[0,1\right]$,
if $\sum_{i=1}^{N}x_{i}\in\left[0,1\right]$, then $\iota\left(\sum_{i=1}^{N}x_{i}\right)\subseteq\sum_{i=1}^{N}\iota\left(x_{i}\right)$. 
\end{itemize}
Moreover, $\iota$ is called convex if for any three numbers\nb$x_{0}$,
$x_{1}$, and $x_{2}\in\left[0,1\right]$, $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$
implies $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.\end{definition}

Although a convex interval-valued function\nb$\iota$ may look exotic,
its left end, defined by $\iotal\left(x\right)=\min\iota\left(x\right)$,
is well-studied Wright-convex satisfying $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,Pales2013}.
After we define interval-valued function, we are ready to construct
a QIVPM from a quantum probability measure.

\begin{lemma}\label{lemma:real2interval}Consider an additive interval-valued
function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$. Then,
given a quantum probability measure\nb$\mu:\events\rightarrow\left[0,1\right]$,
a function\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined by
$\bar{\mu}\left(P\right)=\iota\left(\mu\left(P\right)\right)$ is
a quantum IVPM. Moreover, if $\iota$ is convex, then $\bar{\mu}$
is convex.\end{lemma}

@@

\begin{lemma}Consider an additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
Then, there is a quantum IVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$
such that $\mathrm{core}\left(\bar{\mu}\right)$ has an unique element.
Obviously, if $\iota$ is convex, so does $\bar{\mu}$.\end{lemma}

@@

\begin{example}\label{ex:regular-pair}For any positive integer~$n$,
there is an additive interval-valued function\nb$\iota_{n}:\left[0,1\right]\rightarrow\mathscr{I}_{n}$
defined by
\begin{equation}\eqalign{ 
\mathscr{I}_{n} = \set{\left[\frac{k}{n},\frac{k}{n}\right]}{k=0,\ldots,n}\cup\set{\left[\frac{k}{n},\frac{k+1}{n}\right]}{k=0,\ldots,n-1}\\ 
\iota_{n}\left(x\right) = \cases{ 
\left[\frac{k}{n},\frac{k}{n}\right] & , if $x=\frac{k}{n}$ ;\\ 
\left[\frac{k}{n},\frac{k+1}{n}\right] & , if $\frac{k}{n}<x<\frac{k+1}{n}$ . 
} 
}\end{equation}
Notice that the usual $\left\{ \necess,\imposs,\unknown\right\} $
is $\mathscr{I}_{1}$. Also, let $\mathscr{I}_{\infty}=\set{\left\{ x\right\} }{x\in\left[0,1\right]}$
and $\iota_{\infty}\left(x\right)=\left\{ x\right\} $. Of course,
$\iota_{\infty}:\left[0,1\right]\rightarrow\mathscr{I}_{\infty}$
is an additive interval-valued function.\end{example}

@@

Although a convex QIVPM can be constructed by a convex interval-valued
function easily, its range either is $\left\{ \necess,\imposs,\unknown\right\} $
or contains infinitely many intervals. The reason is that a Wright-convex
function is midpoint-convex or Jensen-convex, i.e., 
\begin{equation}
\frac{\iotal\left(x_{0}\right)+\iotal\left(x_{1}\right)}{2}\ge\iotal\left(\frac{x_{0}+x_{1}}{2}\right)\textrm{ ,}
\end{equation}
and a midpoint-convex function is continuous on an open interval if
we cannot use the Axiom of Choices\nb\cite{Blumberg_1919,Sierpinski1920,RobertsVarberg1973}.

Even if an additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is not convex, it may still induce a convex QIVPM. In particular,
every QIVPM on a three-dimensional Hilbert space is convex by theorem~\ref{thm:convex-3}.
The next natural question is whether a non-convex interval-valued
function always induces some non-convex QIVPM, and the answer is ``yes''
by the following lemma.

\begin{lemma}Given an additive but non-convex interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$,
there is a non-convex quantum IVPM\nb$\bar{\mu}:\events\rightarrow\mathscr{I}$.\end{lemma}

@@

In conclusion, we may still use an additive but non-convex interval-valued
function to construct QIVPMs, but we need to verify the convexity
of the constructed QIVPM one-by-one which might be long and tedious.
